### 2018-07-06 dissertation/5-simulations/chapter5.tex
updated results chapter with better graph positioning

\chapter{Evaluation}
\label{chap:simulations}

@@

%The datasets available from SNAP's website were used for the simulations in \citep{vernize2015malicious} and the static network simulations shown in \Cref{chap:simulations}.
%\\
\textbf{The ONE Simulator}

@@

\Cref{fig:random103050} shows the results of simulations running with 10\% of nodes acting maliciously, with communications range varying from 10m to 50m.
It is possible to see how the increase in the range allows the algorithm to produce better results.
At $\rho = 10$m and $\delta = 0.0017$, a large amount of time is spent with only about half of malicious nodes being accurately identified.
Results with $\rho = 30$m and $\delta = 0.0153$ are better, but still less than ideal; during this simulation, there were more false positive detections happening, although it was still a small amount.
At $\rho = 50$m and $\delta = 0.0427$, results are solid before the 2000th iteration of the algorithm, since at that point over 90\% of the network has been acknowledged by most nodes.
The amount of false positive detections is extremely low, and, by the end of the simulation, all benign nodes have identified 100\% of malicious nodes.

@@

\Cref{fig:randommalicious1} and \Cref{fig:randommalicious2} show the variation of results for different amounts of malicious nodes in the network.
By the end of one day, the algorithm is able to detect all malicious nodes when they are up to 30\% of the network, although there is still a small amount of false positive detections.
At 40\%, a small part of malicious nodes are yet to be detected and the standard deviation is larger overall.
At 50\%, as expected, the results are inconsistent as the network is completely split between benign and malicious nodes; at this point, the network is considered completely compromised.
True positive and false positive detections are often inverted, because whenever there are more malicious nodes than benign one in a certain node's network model, the algorithm will classify the malicious ones as correct.
The amount of malicious nodes also affects how quickly nodes are able to acquire information about the network, since nodes do not trust information from malicious neighbors.

All simulations were performed with trust threshold $h=0.5$, except for the ones in \Cref{fig:randomthresholds}, performed to demonstrate the impact of different threshold values.
The plots illustrate that there is not a significance change in results depending on the different thresholds.
The results are slightly better at $h=0.7$, however not in a significant way.
It still takes over 8000 iterations to detect all malicious nodes and there are still some false positive detections.

@@

\Cref{fig:extramaliciousaging1} and \Cref{fig:extramaliciousaging2} show how TruMan reacts to one node converting from benign to malicious.
These were the only simulations to consider information aging.
Here, several different values for the maximum age, $m$, were tested.
For the simulation, information timestamps are set as the iteration in which they were added to the graph ($s \gets i$), and the age is calculated as the difference between the current iteration and the timestamp ($age \gets i - s$).
With $m=10$, information is discarded too quickly, resulting in highly imprecise results.
Starting with $m=250$, results are reasonable, and the additional malicious node is detected approximately 250 iterations after it converts.
With higher values such as $m=1000$, detection takes longer, but not much else changes. 
When the value is very high, like in the case of $m=5000$, the extra malicious node is not detected by the end of one simulated day.

@@

\begin{table}[t!]
\caption{Properties of the related work}
\label{table:properties_truman}
\centering
\begin{tabular}{|p{4cm}||p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|}
 \hline
 \textbf{Property} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
 \hline
 \hline
 TruMan & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & - & \checkmark \\
 \hline
 \citep{dotzer2005vars} & \checkmark & - & \checkmark & - & - & - & \checkmark & -\\
 \hline
 \citep{minhas2010towards} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & -\\
 \hline
 \citep{chen2010trust} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & -\\
 \hline
 \citep{park2011long} & - & - & - & - & - & \checkmark & \checkmark & \checkmark \\
 \hline
 \citep{huang2014social} & \checkmark & - & \checkmark & \checkmark & \checkmark & - & - & -\\
 \hline
 \citep{li2016art} & \checkmark & - & - & - & \checkmark & - & - & \checkmark\\
 \hline
 \citep{chen2017cloud} & - & \checkmark & - & \checkmark & - & \checkmark & \checkmark & -\\
 \hline
\end{tabular}
\end{table}

\begin{figure}
\centering

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/10_10.png}
\caption{$\rho$ = 10m.} \label{fig:tarjan0}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/30_10.png}
\caption{$\rho$ = 30m.} \label{fig:tarjan0}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/50_10.png}
\caption{$\rho$ = 50m.} \label{fig:tarjan0}
\end{subfigure}

\caption{Simulation with 10\% malicious nodes and varying values of $\rho$.}
\label{fig:random103050}
\end{figure}

\begin{figure}
\centering

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_1.png}
\caption{1\% malicious.}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_5.png}
\caption{5\% malicious.}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_10.png}
\caption{10\% malicious.}
\end{subfigure}

\caption{Simulation with $\rho$ = 10m and varying percentages of malicious nodes (1\%, 5\% and 10\%).}
\label{fig:randommalicious1}
\end{figure}

\begin{figure}
\centering

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_30.png}
\caption{30\% malicious.}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_40.png}
\caption{40\% malicious.}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_50.png}
\caption{50\% malicious.}
\end{subfigure}

\caption{Simulation with $\rho$ = 10m and varying percentages of malicious nodes (30\%, 40\% and 50\%).}
\label{fig:randommalicious2}
\end{figure}

\begin{figure}
\centering

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/thresholds/03_30_10}
\caption{$h = 0.3$.} \label{fig:threshold03}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/thresholds/05_30_10}
\caption{$h = 0.5$.} \label{fig:threshold05}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/thresholds/07_30_10}
\caption{$h = 0.7$.} \label{fig:threshold07}
\end{subfigure}

\caption{Simulation with 10\% malicious nodes, $\rho = 30$m and varying values of $h$.}
\label{fig:randomthresholds}
\end{figure}

\begin{figure}
\centering

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/extra_malicious/1_10}
\caption{$m = 10$.} \label{fig:extra10}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/extra_malicious/1_250}
\caption{$m = 250$.} \label{fig:extra250}
\end{subfigure}

\caption{Simulation with information aging, with different maximum age values ($m=10, 250$).}
\label{fig:extramaliciousaging1}
\end{figure}

\begin{figure}
\centering

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/extra_malicious/1_1000}
\caption{$m = 1000$.} \label{fig:extra1000}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
\includegraphics[width=\linewidth]{images/plots/extra_malicious/1_5000}
\caption{$m = 5000$.} \label{fig:extra5000}
\end{subfigure}

\caption{Simulation with information aging, with different maximum age values ($m=1000, 5000$).}
\label{fig:extramaliciousaging2}
\end{figure}

>>>>

\chapter{Evaluation of TruMan}
\label{chap:simulations}

@@

%The datasets available from SNAP's website were used for the simulations in \citep{vernize2015malicious} and the static network simulations shown in \Cref{chap:simulations}.
%\\
\vspace{5mm}
\textbf{The ONE Simulator}

@@

%\begin{figure}
%\centering
%
%\begin{subfigure}{0.4\textwidth}
%\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/10_10.png}
%\caption{$\rho$ = 10m.}
%\label{fig:random10}
%\end{subfigure}
%
%\hspace*{\fill} % separation between the subfigures
%
%\begin{subfigure}{0.4\textwidth}
%\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/30_10.png}
%\caption{$\rho$ = 30m.} 
%\label{fig:random30}
%\end{subfigure}

%\begin{subfigure}{0.6\textwidth}
%\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/50_10.png}
%\caption{$\rho$ = 50m.} 
%\label{fig:random50}
%\end{subfigure}
%
%\caption{Simulation of TruMan with 10\% malicious nodes and varying values of $\rho$.}
%\label{fig:random103050}
%\end{figure}

%\begin{figure}
%\centering
%
%	\includegraphics[width=0.6\linewidth]{images/plots/Network_rA_10.0/new_plots/10_10.png}
%	\caption{$\rho$ = 10m.} 
%	
%%\caption{Simulation with 10\% malicious nodes and varying values of $\rho$.}
%\label{fig:random10}
%\end{figure}
%
%\begin{figure}
%\centering
%
%	\includegraphics[width=0.6\linewidth]{images/plots/Network_rA_10.0/new_plots/30_10.png}
%	\caption{$\rho$ = 30m.} 
%	
%%\caption{Simulation with 10\% malicious nodes and varying values of $\rho$.}
%\label{fig:random30}
%\end{figure}

%\end{subfigure}%

%\hspace*{\fill}

%\begin{subfigure}{0.4\textwidth}
%	\centering
%	\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/30_10.png}
%	\caption{$\rho$ = 30m.} 
%	\label{fig:tarjan0}
%\end{subfigure}
%
%\begin{subfigure}{0.6\textwidth}
%\includegraphics[width=0.5\linewidth]{images/plots/Network_rA_10.0/new_plots/50_10.png}
%\caption{$\rho$ = 50m.} \label{fig:tarjan0}
%\end{subfigure}

%\caption{Simulation with 10\% malicious nodes and varying values of $\rho$.}
%\label{fig:random103050}
%\end{figure}

\pagebreak
\Cref{fig:random103050} shows the results of simulations running with 10\% of nodes acting maliciously, with communications range varying from 10m to 50m.
It is possible to see how the increase in the range allows the algorithm to produce better results.
At $\rho = 10$m and $\delta = 0.0017$, a large amount of time is spent with only about half of malicious nodes being accurately identified.
Results with $\rho = 30$m and $\delta = 0.0153$ are better, but still less than ideal; during this simulation, there were more false positive detections happening, although it was still a small amount.
At $\rho = 50$m and $\delta = 0.0427$, results are solid before the 2000th iteration of the algorithm, since at that point over 90\% of the network has been acknowledged by most nodes.
The amount of false positive detections is extremely low, and, by the end of the simulation, all benign nodes have identified 100\% of malicious nodes.

\begin{figure}

\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/10_10.png}
\caption{$\rho$ = 10m.} 
\label{fig:random10}
\end{subfigure}
\hspace*{\fill} % separation between the subfigures
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/30_10.png}
\caption{$\rho$ = 30m.} 
\label{fig:random30}
\end{subfigure}

\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA_10.0/new_plots/50_10.png}
\caption{$\rho$ = 50m.} 
\label{fig:random50}
\end{subfigure}

\caption{Simulation of TruMan with 10\% malicious nodes and varying values of $\rho$.}
\label{fig:random103050}
\end{figure}

%\begin{figure}
%\centering
%
%	\includegraphics[width=0.6\linewidth]{images/plots/Network_rA_10.0/new_plots/50_10.png}
%	\caption{$\rho$ = 50m.} 
%	
%%\caption{Simulation with 10\% malicious nodes and varying values of $\rho$.}
%\label{fig:random50}
%\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=0.5\linewidth]{images/plots/Network_rA_10.0/new_plots/10_10.png}
%\caption{$\rho$ = 10m.} \label{fig:tarjan0}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=0.5\linewidth]{images/plots/Network_rA_10.0/new_plots/30_10.png}
%\caption{$\rho$ = 30m.} \label{fig:tarjan1}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=0.5\linewidth]{images/plots/Network_rA_10.0/new_plots/50_10.png}
%\caption{$\rho$ = 50m.} \label{fig:tarjan2}
%\end{figure}

@@

\pagebreak
\Cref{fig:randommalicious1} and \Cref{fig:randommalicious2} show the variation of results for different amounts of malicious nodes in the network.
By the end of one day, the algorithm is able to detect all malicious nodes when they are up to 30\% of the network, although there is still a small amount of false positive detections.
At 40\%, a small part of malicious nodes are yet to be detected and the standard deviation is larger overall.
At 50\%, as expected, the results are inconsistent as the network is completely split between benign and malicious nodes; at this point, the network is considered completely compromised.
True positive and false positive detections are often inverted, because whenever there are more malicious nodes than benign one in a certain node's network model, the algorithm will classify the malicious ones as correct.
The amount of malicious nodes also affects how quickly nodes are able to acquire information about the network, since nodes do not trust information from malicious neighbors.

\begin{figure}

\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_1.png}
\caption{1\% malicious.}
\end{subfigure}
\hspace*{\fill} % separation between the subfigures
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_5.png}
\caption{5\% malicious.}
\end{subfigure}

\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_10.png}
\caption{10\% malicious.}
\end{subfigure}

\caption{Simulation of TruMan with $\rho$ = 10m and varying percentages of malicious nodes (1\%, 5\% and 10\%).}
\label{fig:randommalicious1}
\end{figure}

\begin{figure}

\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_30.png}
\caption{30\% malicious.}
\end{subfigure}
\hspace*{\fill} % separation between the subfigures
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_40.png}
\caption{40\% malicious.}
\end{subfigure}

\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/Network_rA/10_50.png}
\caption{50\% malicious.}
\end{subfigure}

\caption{Simulation of TruMan with $\rho$ = 10m and varying percentages of malicious nodes (30\%, 40\% and 50\%).}
\label{fig:randommalicious2}
\end{figure}

\pagebreak
All simulations were performed with trust threshold $h=0.5$, except for the ones in \Cref{fig:randomthresholds}, performed to demonstrate the impact of different threshold values.
The plots illustrate that there is not a significance change in results depending on the different thresholds.
The results are slightly better at $h=0.7$, however not in a significant way.
It still takes over 8000 iterations to detect all malicious nodes and there are still some false positive detections.

\begin{figure}

\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/thresholds/03_30_10}
\caption{$h = 0.3$.} \label{fig:threshold03}
\end{subfigure}
\hspace*{\fill} % separation between the subfigures
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/thresholds/05_30_10}
\caption{$h = 0.5$.} \label{fig:threshold05}
\end{subfigure}

\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/thresholds/07_30_10}
\caption{$h = 0.7$.} \label{fig:threshold07}
\end{subfigure}

\caption{Simulation of TruMan with 10\% malicious nodes, $\rho = 30$m and varying values of $h$.}
\label{fig:randomthresholds}
\end{figure}

@@

\begin{figure}

\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/extra_malicious/1_10}
\caption{$m = 10$.} \label{fig:extra10}
\end{subfigure}
\hspace*{\fill} % separation between the subfigures
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/extra_malicious/1_250}
\caption{$m = 250$.} \label{fig:extra250}
\end{subfigure}

\centering
\caption{Simulation of TruMan with information aging, with different maximum age values ($m=10, 250$).}
\label{fig:extramaliciousaging1}
\end{figure}

\begin{figure}

\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/extra_malicious/1_1000}
\caption{$m = 1000$.} \label{fig:extra1000}
\end{subfigure}
\hspace*{\fill} % separation between the subfigures
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\linewidth]{images/plots/extra_malicious/1_5000}
\caption{$m = 5000$.} \label{fig:extra5000}
\end{subfigure}

\centering
\caption{Simulation with information aging, with different maximum age values ($m=1000, 5000$).}
\label{fig:extramaliciousaging2}
\end{figure}

\pagebreak
\Cref{fig:extramaliciousaging1} and \Cref{fig:extramaliciousaging2} show how TruMan reacts to one node converting from benign to malicious.
These were the only simulations to consider information aging.
Here, several different values for the maximum age, $m$, were tested.
For the simulation, information timestamps are set as the iteration in which they were added to the graph ($s \gets i$), and the age is calculated as the difference between the current iteration and the timestamp ($age \gets i - s$).
With $m=10$, information is discarded too quickly, resulting in highly imprecise results.
Starting with $m=250$, results are reasonable, and the additional malicious node is detected approximately 250 iterations after it converts.
With higher values such as $m=1000$, detection takes longer, but not much else changes. 
When the value is very high, like in the case of $m=5000$, the extra malicious node is not detected by the end of one simulated day.

@@

\begin{table}[hpbt!]
\caption{Properties of the related work}
\label{table:properties_truman}
\centering
\begin{tabular}{|p{4cm}||p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|}
 \hline
 \textbf{Property} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
 \hline
 \hline
 TruMan & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & - & \checkmark \\
 \hline
 \citep{dotzer2005vars} & \checkmark & - & \checkmark & - & - & - & \checkmark & -\\
 \hline
 \citep{minhas2010towards} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & -\\
 \hline
 \citep{chen2010trust} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & -\\
 \hline
 \citep{park2011long} & - & - & - & - & - & \checkmark & \checkmark & \checkmark \\
 \hline
 \citep{huang2014social} & \checkmark & - & \checkmark & \checkmark & \checkmark & - & - & -\\
 \hline
 \citep{li2016art} & \checkmark & - & - & - & \checkmark & - & - & \checkmark\\
 \hline
 \citep{chen2017cloud} & - & \checkmark & - & \checkmark & - & \checkmark & \checkmark & -\\
 \hline
\end{tabular}
\end{table}
